A 30 Million Year Old Mini-Neptune in the Kepler Field

### 2021-05-18 paper/ms.tex
update ms

\newcommand{\cn}{$\delta$~Lyr\ cluster} % cluster name
\newcommand{\sn}{Kepler\,1627} % star system name (binary)
\newcommand{\pn}{Kepler\,1627Ab} % plane name

@@

>>>>

\newcommand{\cn}{$\delta$~Lyr\ cluster} % cluster name
\newcommand{\sn}{Kepler\,1627} % star system name (binary)
\newcommand{\pn}{Kepler\,1627Ab} % planet name

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf \sn\ light curve over 100 days.}  
    The full Kepler dataset spans 1{,}437 days (3.9 years), sampled at
    30 minute cadence.  The {\it top panel} shows the largest
    signal, induced by starspots and plages.  The model for the
    stellar variability (orange line) is subtracted in the {\it
    bottom panel}, highlighting the transits of \pn, as well as other
    deviations from the stellar variability model.  The 
    Figure Set available online shows the entire 3.9 years of
    available data.
		\label{fig:lightcurve}
	}
\end{figure*}
